Rapid Epidemiological Analysis of Comorbidities and Treatments in COVID-19 in Scotland (REACT-SCOT): a case-control study based on the Scottish population

### 2020-05-14 casecontrol.Rmd
Corrected author names.

---
title: 'Rapid Epidemiological Analysis of Comorbidities and Treatments in COVID-19 in Scotland (REACT-SCOT): a case-control study based on the Scottish population'
author: 
  - name: Paul M McKeigue
    email: paul.mckeigue@ed.ac.uk
    affiliation: Usher
  - name: Amanda Weir 
    affiliation: HPS
  - name: Jen Bishop
    affiliation: HPS
  - name: Stuart McGurnaghan
    affiliation: IGMM
  - name: Sharon Kennedy
    affiliation: HPS
  - name: David McAllister 
    affiliation: Glasgow
  - name: Chris Robertson 
    affiliation: Strathclyde
  - name: Rachael Wood
    affiliation: ISD
  - name: Nazir Lone
    affiliation: Usher
  - name: Janet Murray
    affiliation: HPS 
  - name: Tom Caparrotta 
    affiliation: IGMM
  - name: Sharon Hutchinson 
    affiliation: GCU
  - name: Helen M Colhoun
    affiliation: IGMM
address: 
   - code: Usher
     address: Usher Institute, College of Medicine and Veterinary Medicine, University of Edinburgh, Teviot Place, Edinburgh EH8 9AG, Scotland. PM - Professor of Genetic Epidemiology and Statistical Genetics. NL - Clinical Senior Lecturer in Critical Care
   - code: IGMM
     address: Institute of Genetics and Molecular Medicine, College of Medicine and Veterinary Medicine, University of Edinburgh, Western General Hospital Campus, Crewe Road, Edinburgh EH4 2XUC, Scotland. HC - Axa Chair in Medical Informatics and Epidemiology. TC - Sir George Alberti Doctoral Fellow in Pharmacoepidemiology. 
   - code: Glasgow
     address: Institute of Health and Wellbeing, University of Glasgow, 1 Lilybank Gardens, Glasgow G12 8RZ. DM - Senior Clinical Lecturer in Public Health 
   - code: HPS
     address: Health Protection Scotland (Public Health Scotland), Meridian Court, 5 Cadogan Street, Glasgow G2 6QE
   - code: Strathclyde
     address: Department of Mathematics and Statistics, University of Strathclyde, 16 Richmond Street, Glasgow G1 1XQ. CR - Professor of Public Health Epidemiology
   - code: GCU
     address: School of Health and Life Sciences, Glasgow Caledonian University. SH - Professor of Epidemiology and Population Health 
   - code: ISD
     address: NHS Information Services Division (Public Health Scotland), Gyle Square, 1 South Gyle Crescent, Edinburgh, EH12 9EB.  RW - Consultant in Maternal and Child Health. 
geometry: margin=1in
fontsize: 11pt
linenumbers: true
bibliography: ../covid.bib
date: "This version compiled `r gsub('^0', '', format(Sys.time(), '%d %B %Y'))`"
header-includes: |
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{lscape}
output: 
#  pdf_document:
  rticles::plos_article:
    latex_engine: lualatex
    fig_caption: true
    keep_tex: true
#    toc: true
#    toc_depth: 2
csl: ../plos.csl
urlcolor: red

>>>>

---
title: 'Rapid Epidemiological Analysis of Comorbidities and Treatments in COVID-19 in Scotland (REACT-SCOT): a case-control study based on the Scottish population'
author: 
  - name: Paul M McKeigue
    email: paul.mckeigue@ed.ac.uk
    affiliation: Usher
  - name: Amanda Weir 
    affiliation: HPS
  - name: Jen Bishop
    affiliation: HPS
  - name: Stuart J McGurnaghan
    affiliation: IGMM
  - name: Sharon Kennedy
    affiliation: HPS
  - name: David McAllister 
    affiliation: Glasgow
  - name: Chris Robertson 
    affiliation: Strathclyde
  - name: Rachael Wood
    affiliation: ISD
  - name: Nazir Lone
    affiliation: Usher
  - name: Janet Murray
    affiliation: HPS 
  - name: Thomas M Caparrotta 
    affiliation: IGMM
  - name: Sharon Hutchinson 
    affiliation: GCU
  - name: Helen M Colhoun
    affiliation: IGMM
address: 
   - code: Usher
     address: Usher Institute, College of Medicine and Veterinary Medicine, University of Edinburgh, Teviot Place, Edinburgh EH8 9AG, Scotland. PM - Professor of Genetic Epidemiology and Statistical Genetics. NL - Clinical Senior Lecturer in Critical Care
   - code: IGMM
     address: Institute of Genetics and Molecular Medicine, College of Medicine and Veterinary Medicine, University of Edinburgh, Western General Hospital Campus, Crewe Road, Edinburgh EH4 2XUC, Scotland. HC - Axa Chair in Medical Informatics and Epidemiology. TC - Sir George Alberti Doctoral Fellow in Pharmacoepidemiology. 
   - code: Glasgow
     address: Institute of Health and Wellbeing, University of Glasgow, 1 Lilybank Gardens, Glasgow G12 8RZ. DM - Senior Clinical Lecturer in Public Health 
   - code: HPS
     address: Health Protection Scotland (Public Health Scotland), Meridian Court, 5 Cadogan Street, Glasgow G2 6QE
   - code: Strathclyde
     address: Department of Mathematics and Statistics, University of Strathclyde, 16 Richmond Street, Glasgow G1 1XQ. CR - Professor of Public Health Epidemiology
   - code: GCU
     address: School of Health and Life Sciences, Glasgow Caledonian University. SH - Professor of Epidemiology and Population Health 
   - code: ISD
     address: NHS Information Services Division (Public Health Scotland), Gyle Square, 1 South Gyle Crescent, Edinburgh, EH12 9EB.  RW - Consultant in Maternal and Child Health. 
geometry: margin=1in
fontsize: 11pt
linenumbers: true
bibliography: ../covid.bib
date: "This version compiled `r gsub('^0', '', format(Sys.time(), '%d %B %Y'))`"
header-includes: |
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{lscape}
output: 
#  pdf_document:
  rticles::plos_article:
    latex_engine: lualatex
    fig_caption: true
    keep_tex: true
#    toc: true
#    toc_depth: 2
csl: ../plos.csl
urlcolor: red
